---
title: "Flammulated Owl Fall Prospecting Analysis"
author: "Scott Yanco"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: "show"
    css: style.css 
    toc: true
    toc_float: true
    theme: sandstone
    includes:
      before_body: header.html 
      after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy = FALSE)
```


#Required Libraries

```{r message=FALSE, warning=FALSE}
# devtools::install_github("cardiomoon/ggiraphExtra")
# devtools::install_github('oswaldosantos/ggsn')
# devtools::install_github("3wen/legendMap")

#data mgmt
library(tidyverse) 
library(reshape2)

#plotting
library(ggplot2)
library(ggmosaic)
library(wesanderson)
library(png)
library(grid)
library(ggiraphExtra)
library(gridExtra)
library(egg)
library(ggthemes)

#inference
library(lme4)
library(AICcmodavg)

#spatial
library(rgdal)
library(sf)
library(ggspatial)
library(ggmap)
library(maptools)
library(broom)
library(tmap)
library(ggsn)
library(legendMap)
library(rnaturalearth)
library(rnaturalearthdata)


```

# Custom Functions

```{r}
#add custom annotations to ggplots
annotation_custom2 <- 
  function (grob, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, data) 
  {
    layer(data = data, stat = StatIdentity, position = PositionIdentity, 
          geom = ggplot2:::GeomCustomAnn,
          inherit.aes = TRUE, params = list(grob = grob, 
                                            xmin = xmin, xmax = xmax, 
                                            ymin = ymin, ymax = ymax))
  }

#Make function to calculate straight-line distance from X,Y coords 
calc_dist <- function(x_1, y_1, x_2, y_2) {
  x_dist <- abs(x_1-x_2)
  y_dist <- abs(y_1-y_2)
  dist <- sqrt((x_dist^2)+(y_dist^2))
  return(dist)
}

#get pvalue from a given normal distribution
probAssign <- function(dD, mean, sd) {
  pval <- pnorm(dD, mean = mean, sd = sd, lower.tail = F)
}

```

```{r}
#create color palette
pal <- c("#3B9AB2", "#EBCC2A")
```


# Initial Data Import, Cleaning, and Management 

## Load and clean dD dataset

```{r}
#read in the raw iso data .csv
owl_deut <- read.csv("data/owl_dD.csv", stringsAsFactors = F)

#replace two cases of missing band #s
#UPDATE THIS - right now this just removes the last two rows...
owl_deut <- owl_deut[1:(nrow(owl_deut)-2),] 

#create new identifier that removes the beginning "o"
id2 <- substring(owl_deut$indentifier, 2)

#create a feather type column that extracts the final letter from the identifier
owl_deut$iso_feath_type <- substr(owl_deut$indentifier,
                                  nchar(owl_deut$indentifier), #start at last
                                  nchar(owl_deut$indentifier)) #stop at last

#write new band column with band number only
owl_deut$band <- substr(id2,1,nchar(id2)-1)

#extract band suffix and add to df
owl_deut$suffix <- as.integer(gsub("(^\\d+\\-)","" ,owl_deut$band))

#extract band prefix and add to df
owl_deut$prefix <- as.integer(gsub("(\\-\\d+$)","" ,owl_deut$band))
```

Merge the capture and morph datasets into the isotope data set - start by pulling in the fall-only data

```{r}
#load dataset
fall_band <- read.csv("data/fall_band.csv", stringsAsFactors = F)

#merge data frames based on the 3 band columns
owl_comb <- merge(owl_deut, fall_band, by.x = c("band", "suffix", "prefix"),
                  by.y = c("Index.Band", "Suffix", "Prefix"), 
                  all = T)

#update status column for breeding season captures of known residents
owl_comb$ID[is.na(owl_comb$ID)] <- "BR"
```

Next step is to bring in some necessary data from the MEF band dataset for the BR birds.

```{r}
#read in MEF band data as of 2018 field season
mef_band <- read.csv("data/mef_band_2018.csv")

#extract the rows of the MEF data whose band number match those in owl_comb
mef_deut <- mef_band[mef_band$Band.Prefix %in% owl_comb$prefix &
                       mef_band$Band.Suffix %in% owl_comb$suffix,]

#Fill in missing age data from MEF BR birds
#first create data frame of the sex and age values for the 26 MEF BNR birds
missingMEF <- data.frame(
  "Age" = mef_deut$Age[which(mef_deut$Band.Suffix %in% 
                               owl_comb$suffix[is.na(owl_comb$PAge)])],
  "Sex" = mef_deut$Sex[which(mef_deut$Band.Suffix %in% 
                               owl_comb$suffix[is.na(owl_comb$Sex)])],
  "prefix" = mef_deut$Band.Prefix[which(mef_deut$Band.Suffix %in% 
                                          owl_comb$suffix[is.na(owl_comb$Sex)])],
  "suffix" = mef_deut$Band.Suffix[which(mef_deut$Band.Suffix %in% 
                                          owl_comb$suffix[is.na(owl_comb$Sex)])]
)

#merge MEf birds into owl_comb  
owl_comb <- merge(owl_comb, missingMEF, by = c("prefix", "suffix"), all.x = T, 
                  no.dups = T)
owl_comb$age <- ifelse(!is.na(owl_comb$PAge), owl_comb$PAge,
                       as.character(owl_comb$Age.y))
owl_comb$sex <- ifelse(!is.na(owl_comb$Sex.x), owl_comb$Sex.x, 
                       as.character(owl_comb$Sex.y))
```

A bit more cleaning and combining - get combined age and sex columns

```{r}
#make a function to assign a "local" or "unknown" status
makeorigin <-Vectorize(function(x) {
  switch(x, "RA" = "local", "NR" = "local",
         "RY" = "local", "U" = "unknown", "F" = "unknown",
         "PF" = "unknown", "BR" = "local")
}, "x")

#apply function and put results in new column of owl_comb
owl_comb$origin <- as.factor(makeorigin(owl_comb$ID))

#change date format
owl_comb$Date <- as.Date(owl_comb$Date, format = "%d/%m/%Y")

#fix age column
owl_comb$age[owl_comb$age == "2"] <- "AHY"
owl_comb$age[owl_comb$age == "3"] <- "AHY"
owl_comb$age[owl_comb$age == ""] <- NA
owl_comb$age[owl_comb$age == "Ad"] <- "AHY"
owl_comb$age[owl_comb$age == "AD"] <- "AHY"
owl_comb$age[owl_comb$age == "A"] <- "AHY"
owl_comb$age[owl_comb$age == "FL"] <- "HY"
owl_comb$age[owl_comb$age == "L"] <- "HY"
owl_comb$age[owl_comb$age == "Y"] <- "HY"
```

# Compare double measured birds 

This section analyzes birds for which we have two feather isotope values for different feather types.  This helps us evaluate the use of juvenile contour feathers in analyses that otherwise include adult remiges.

```{r}
#extract from the complete dataset only those individuals with dD values
deut_data <- owl_comb[!is.na(owl_comb$dD),]

#need to remove duplicated dD data for birds captured twice in a season
deut_data <- distinct(deut_data, band, analysis, .keep_all = T)

#extract all the double measured individuals by keeping only duplicated bands
doubles <- deut_data[duplicated(deut_data$band) | duplicated(deut_data$band, 
                                                             fromLast = T),] 
#sort by band number and then feather type
doubles <- doubles[order(doubles$band, doubles$iso_feath_type),] 

# #remove single case with 2 juv feathers and no primary
# doubles <- filter(doubles, doubles$band != "1833-03340") 

#convert to factors
doubles$band <- as.factor(doubles$band)
```

Now we take the difference in $\delta D$ values between paired measurements from single individuals.

```{r}
difs <- c()
for (i in 1:length(unique(doubles$band))) {
  #first, make sure there are no records using the same feather types
  if(any(doubles$iso_feath_type[doubles$band == 
                                unique(doubles$band)[i]] == "j") &
     any(doubles$iso_feath_type[doubles$band == 
                                unique(doubles$band)[i]] == "p")){
    difs[i] <- doubles$dD[doubles$band == unique(doubles$band)[i] 
                          & doubles$iso_feath_type == "j"] - 
      doubles$dD[doubles$band == unique(doubles$band)[i] &
                   doubles$iso_feath_type == "p"]
  } 
}

difs <- data.frame(dD = na.omit(difs), 
                   pos = seq(from = .1, by = .1,   
                             length.out = length(na.omit(difs))))

```

Descriptive numbers:

```{r}
max(abs(difs$dD))
min(abs(difs$dD))
```

We now make a plot showing the distribution of differences.

```{r}
(difs_plot <- ggplot(data = difs) +
   #geom_jitter(aes(x = 1, y = dD), width = .1) +
   geom_point(aes(x = pos, y = dD)) +
   geom_errorbar(aes(x = pos, y = dD, ymax = dD + 8, ymin = dD - 8),
                 width = .1) +
   geom_hline(yintercept = 0, linetype = "dashed") +
   #xlim(c(0.5, 1.5)) +
   ylim(c(-30, 30)) +
   ylab(expression(paste("Difference in ", delta^"2", "D", sep = ""))) +
   theme_classic() +
   theme(axis.text.x = element_blank(), 
         axis.ticks.x = element_blank(), 
         axis.title.x = element_blank()))

ggsave(difs_plot, file = "figures/difs_plot.png", dpi = 400)
```

# Isotope analyis for known- and unknown-origin birds
First we need to remove those values for which age is unknown since AHy and HY have differnet dD values.

```{r}
deut_data_age <- deut_data[!is.na(deut_data$age),]
```

Start by removing the double-measured unknown birds - get rid of juvenile feathers when possible

```{r}
#sort by band number and then feather type
deut_origin <- deut_data_age[order(deut_data_age$band, 
                                   deut_data_age$iso_feath_type),] 

#extract all the double measured individuals by keeping only duplicated bands
deut_origin <- deut_origin[!duplicated(deut_data_age$band, fromLast = T),]

#print some sub-sample sizes
#local and unknown birds with isos
nrow(deut_origin[deut_origin$origin == "local",])
nrow(deut_origin[deut_origin$origin == "unknown",])

#age breakdown of local birds
nrow(deut_origin[deut_origin$origin == "local" & deut_origin$age == "HY",])
nrow(deut_origin[deut_origin$origin == "local"& deut_origin$age == "AHY",])

#age breakdown of unknown birds
nrow(deut_origin[deut_origin$origin == "unknown" & deut_origin$age == "HY",])
nrow(deut_origin[deut_origin$origin == "unknown"& deut_origin$age == "AHY",])
```

Histograms of dD by origin, facet by age.

```{r}
#plot faceted histograms with rug plot
deut_age_origin <- ggplot(data = deut_origin) +
  stat_density(aes(x = dD, linetype = origin), geom="path", 
               position = "identity") +
  #geom_rug(aes(x = dD, color = origin)) +
  #scale_color_manual(values = pal) +
  xlab(expression(paste(delta^"2", "D", sep = ""))) +
  scale_y_continuous(breaks=seq(0,.06,.05)) +
  theme_classic() +
  facet_wrap(~age) +
  ylab("Density") +
  labs(linetype = "Origin")

deut_age_origin
```

## Probability-based assignments

First we need to get the distributional parameters of the known-orgins birds by age class.

```{r}
#pull out local only
deut_local <- deut_origin[deut_origin$origin == "local",]

mean_hy <- mean(deut_local$dD[deut_local$age == "HY"])
sd_hy <- sd(deut_local$dD[deut_local$age == "HY"])

mean_ahy <- mean(deut_local$dD[deut_local$age == "AHY"])
sd_ahy <- sd(deut_local$dD[deut_local$age == "AHY"])

param_df <- data.frame("age" = c("HY", "AHY"),
                       "mean" = c(mean_hy, mean_ahy),
                       "sd" = c(sd_hy, sd_ahy))
```

Now we can use those parameters to assume a normal distribution for the known-origin birds for each age class and then assess the probability of each unknown-origin individual having come from the associated known-origin distribution. First, to make this computationally simple, we'll just separate the HY from AHY birds.

```{r}
deut_hy <- deut_origin[deut_origin$age == "HY" & 
                         deut_origin$origin == "unknown",]
deut_ahy <- deut_origin[deut_origin$age == "AHY" & 
                          deut_origin$origin == "unknown",]

```

Now we can pull the respective probabilities

```{r}
deut_prob_hy <- sapply(deut_hy$dD, probAssign, mean = mean_hy, sd = sd_hy)

deut_prob_ahy <- sapply(deut_ahy$dD, probAssign, mean = mean_ahy, sd = sd_ahy)

deut_probs <- data.frame("prob" = c(deut_prob_hy, deut_prob_ahy), 
                         "age" = c(rep("HY", length(deut_prob_hy)),
                                   rep("AHY", length(deut_prob_ahy))),
                         "dD" = c(deut_hy$dD, deut_ahy$dD))
deut_probs$sig <- sapply(deut_probs$prob, function(x) {
  if(x>= 0.975 | x <= 0.025){
    return("sig")
  } else {
    return("nonsig")
  }
  
})

```

```{r }
deut_probs$dD[deut_probs$prob < .025 | deut_probs$prob > .975]
deut_probs$prob[deut_probs$prob < .025 | deut_probs$prob > .975]

```

```{r}
ggplot() +
  geom_jitter(data = deut_probs, 
              aes(y = dD, x = 0.5, shape = sig), 
              position = position_jitter(0.4)) +
  scale_shape_manual(values = c(16, 8)) +
  geom_segment(data = param_df, 
               aes(x = .1, xend = 1, y = qnorm(0.975, mean = mean, sd = sd), 
                   yend = qnorm(0.975, mean = mean, sd = sd)), 
               linetype = "twodash", xmin = .1) +
  
  # geom_hline(data = param_df, 
  #            aes(yintercept = qnorm(0.975, mean = mean, sd = sd)), 
  #            linetype = "twodash", xmin = .1) +
  # geom_hline(data = param_df, 
  #            aes(yintercept = qnorm(0.025, mean = mean, sd = sd)), 
  #            linetype = "twodash") +
  geom_segment(data = param_df, 
               aes(y = qnorm(0.025, mean = mean, sd = sd), 
                   yend = qnorm(0.025, mean = mean, sd = sd), x = .1, xend = 1), 
               linetype = "twodash") +
  ylab(expression(paste(delta, "D", sep = ""))) +
  theme_classic() +
  xlab("") +
  theme(axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        legend.position = "none") +
  facet_wrap(~age)
```

# Fall to Breeding Individuals

Fall birds recaptured as breeders in subsequent years relative to the dD distributions.

```{r}
#vector of F2S band numbers
falltosummer <- c("1783-64429","1833-03191","1783-64490","1783-64452",
                  "1833-03104","1833-03116","1833-03309","1833-03322",
                  "1833-03307","1783-74351","1833-03329","1833-03417")
#read in owl graphic and transform to rasterGrob object
owl <- readPNG("art/FLOW Line Drawing.png")
imgl <- list(owl, owl)
#g1 <- rasterGrob(owl, interpolate=FALSE)
#get the dD values for F2S birds
recap_deut <- deut_data$dD[which(deut_data$band %in% falltosummer)]
recap_deut <- data.frame(deut = recap_deut, age = c("HY", "AHY"))
#need to reverse order for faceting below
recap_deut <- recap_deut[nrow(recap_deut):1,]
recap_deut$pic <- I(imgl)

#get band numbers of the F2S birds for which we have dD values
recap_bands <- data.frame(bands = deut_data$band[which(deut_data$band %in%
                                                         falltosummer)])
recap_bands <- data.frame(bands = recap_bands, age = c("HY", "AHY"))

#need to reverse order for faceting below

#recap_bands <- recap_bands[nrow(recap_bands):1,]

recap_iso_birds <- deut_data[which(deut_data$band %in% falltosummer),]
recap_iso_birds

deut_data_age$age <- factor(deut_data_age$age)

pal4 <- wes_palette("Zissou1", 4, "discrete")
```

```{r}
#plot
(deut_cap <- ggplot() +
   stat_density(data = deut_origin, 
                aes(x = dD, linetype = origin), geom = "path",
                position = "identity") +
   facet_wrap(~age, scales = "free_x") +
   # scale_fill_manual(values = pal4) +
   # scale_color_manual(values = pal4) +
   geom_vline(data = recap_deut, aes(xintercept = deut), linetype = "dashed") +
   # geom_text(data = recap_deut, aes(x=deut-4, y = .016, 
   #               label = paste0(recap_bands$bands, " (",
   #                              recap_iso_birds$age,
   #                              ")"), angle = 90)) +
   # annotation_custom(g1,  xmin=c(-90, -70), xmax = c(-50, -50),
   #                   ymin = 0, ymax = .01) +
   # # annotation_custom(g1, xmin=recap_deut$deut[2]-10, xmax = recap_deut$deut[2], 
   #                   ymin = 0, ymax = .01) +
   geom_custom(data = recap_deut, aes(data = pic, x = deut+7), y = .001, 
               grob_fun = rasterGrob, fun_params = list(height= unit(1, "cm"))) +
   xlab(expression(paste(delta, "D", sep = ""))) +
   scale_y_continuous(breaks=seq(0,.06,.05)) +
   ylab("Probability Density") +
   labs(linetype = "Origin") +
   theme_classic() )

ggsave(deut_cap, file ="figures/hist.png", dpi = 400)
# ggsave("owlplot.png", dpi = 400)
```

# dD by Time
Look for evidence of migration picking up late by considering whether dD varies by date. We'll first graph it.

```{r}
#dD by julian date
(deut_by_date <- ggplot(data = deut_data, aes(x = Julian, y = dD)) +
   geom_point() +
   geom_smooth(method = "lm", color = "black") +
   geom_hline(yintercept = mean(deut_data$dD), linetype = "dashed") +
   ylab(expression(paste(delta ^"2", "D", sep = ""))) +
   xlab("Julian Date") +
   scale_y_continuous(breaks=c(-85,-65,-45, -25)) +
   #scale_x_continuous(breaks=c(244,249,255)) +
   theme_classic())

ggsave(deut_by_date, file = "figures/dDbytime.png", dpi = 400)
```

We can also run the linear model for this.

```{r}
#make dataset without NAa
deut_time <- deut_data[!is.na(deut_data$Julian),] #clean out missing data

#fit models
fit.notime <- lm(Julian ~ 1, data = deut_time)
fit.time <- lm(Julian ~ dD, data = deut_time)
# fit.age <- lm(Julian ~ age, data = deut_time)
#only 5 observations


#AIC selection
aictab(list("intercept" = fit.notime, "time by dD" = fit.time))
summary(fit.time)
summary(fit.notime)

confint(fit.time)
# summary(fit.age)
```

Separate the dD over time by age groups for age-known birds.

```{r}
#dD by julian date and age
deut_by_date <- ggplot(data = deut_data_age, aes(x = Julian, y = dD, 
                                                 shape = age, color = age)) +
  geom_point() +
  geom_smooth(method = "lm", aes(color = age)) +
  ylab(expression(paste(delta, "D", sep = ""))) +
  xlab("Julian Date") +
  theme_classic()

deut_by_date
```

Let's also re-run the linear models including an interaction with age.
```{r}
#make datset with no missing values for age or Julian 
deut_data_age_time <- deut_data_age[!is.na(deut_data_age$Julian),]

#fit models
fit.notime <- lm(dD ~ 1, data = deut_data_age_time)
fit.time <- lm(dD ~ Julian, data = deut_data_age_time)
fit.timebyage <- lm(dD ~ Julian*age, data = deut_data_age_time)

aictab(list("intercept" = fit.notime, "time" = fit.time, 
            "time*age" = fit.timebyage))

summary(fit.timebyage)
ggPredict(fit.timebyage,se=TRUE) +
  theme_classic()
```

# Passage Dates
```{r}
owl_comb %>% 
  group_by(sex, origin) %>% 
  summarise(m_pass = median(Julian), r = range(Julian)[1], r2 = range(Julian)[2])

owl_comb %>% 
  group_by(age, origin) %>% 
  summarise(m_pass = median(Julian), r = range(Julian)[1], r2 = range(Julian)[2])
```

# Sex and age ratios
```{r}
owl_comb$sex[owl_comb$sex == "?"] <- "U"
agesex <- ggplot(data = owl_comb[!is.na(owl_comb$age),]) +
  geom_mosaic(aes(x = product(sex, age), fill = sex)) +
  scale_fill_grey(start = 0, end = .9) + 
  theme_bw()
agesex

```

```{r}
#total records
tot <- nrow(owl_comb)

#total fall
f <- sum(owl_comb$origin == "unknown")
f
#num HY
fhy <-sum(na.omit(owl_comb$age == "HY" & owl_comb$origin == "unknown"))
fhy
#num AHY
fahy <- sum(na.omit(owl_comb$age == "AHY" & owl_comb$origin == "unknown"))
fahy
#num unk
funk <- sum(is.na(owl_comb$age[owl_comb$origin == "unknown"]))
funk

fhy/f

fahy/f

funk/f

#sex breakdown
sum(na.omit(owl_comb$age == "AHY" & owl_comb$sex == "F" 
            & owl_comb$origin == "unknown"))
sum(na.omit(owl_comb$age == "AHY" & owl_comb$sex == "M" 
            & owl_comb$origin == "unknown"))

```

```{r}
ggplot(data = owl_comb[owl_comb$origin == "unknown" & !is.na(owl_comb$age),]) +
  geom_boxplot(aes(x = age, y = Julian))

ggplot(data = owl_comb[owl_comb$origin == "unknown" & !is.na(owl_comb$sex),]) +
  geom_boxplot(aes(x = sex, y = Julian))

median(na.omit(owl_comb$Julian[owl_comb$origin == "unknown" & 
                                 owl_comb$age == "HY"]))
median(na.omit(owl_comb$Julian[owl_comb$origin == "unknown" & 
                                 owl_comb$age == "AHY"]))

median(na.omit(owl_comb$Julian[owl_comb$origin == "unknown" & 
                                 owl_comb$sex == "M"]))
median(na.omit(owl_comb$Julian[owl_comb$origin == "unknown" & 
                                 owl_comb$sex == "F"]))

```

# Passage Rates

First let's load the data in and do any cleaning.

```{r}
#need to get net hours by date to normalize this
caprates <- read.csv("data/nethours.csv")

#convert year to factor
caprates$year <- as.factor(caprates$year)

#remove outlier due to very short net run
caprates <- caprates[-which(caprates$cap_per_hr == max(caprates$cap_per_hr)),]
```

summary stats
```{r}
#total median and range
median(caprates$cap_per_hr)
range(caprates$cap_per_hr)
```

Now we can fit a set of linear models to consider any trend in capture rates over time.
```{r}
#Use lm and information theoretics to test hypotheses about rate
#can't do mixed effects because too few data- models don't converge
rate.int <- lm(cap_per_hr ~ 1, data = caprates)
rate.lin <- lm(cap_per_hr ~ julian, data = caprates)
rate.quad <- lm(cap_per_hr ~ poly(julian, 2, raw = T), data = caprates)
aictab(list("intercept" = rate.int, "linear" = rate.lin, 
            "quadratic" = rate.quad))
summary(rate.quad)
summary(rate.int)
summary(rate.lin)

caprates$fit <- predict(rate.quad)
```

Now we're ready to plot the rate over time and we can supply the trendline from our best model (the intercept model).

```{r fig.height=4, fig.width=6}
#plot
cap_rate_plot <- ggplot(data = caprates, aes(x=julian, y = cap_per_hr)) +
  geom_point(aes(group = year, shape = year), colour="black") +
  # scale_shape_manual(values = c(1:4)) +
  # scale_fill_manual(values = wes_palette("FantasticFox1", 4, "discrete")) +
  geom_smooth(method = "lm", color = "black",
              formula = y ~ poly(x, 2, raw = T)) +
  ylab(expression("Captures " ~ hr^{-1})) +
  xlab("Julian Date") +
  labs(shape = "Year") +
  theme_classic()

ggsave(cap_rate_plot, file = "figures/caprate.png", dpi = 400, width = 6, 
       height = 4)
# ggsave("figures/caprate.png", dpi = 400)
```

# Spatial Analyses

First we need to bring in the relevant data.

```{r}
#read in the recapture data
owl_recap <- read.csv("data/recap_wide.csv") %>% 
  left_join(owl_comb, by = "band")

#make lines for each cap-recap pair
recap_lines <- lapply(X=1:nrow(owl_recap), FUN = function(x) {
  pair <- st_linestring(matrix(c(owl_recap$x_1[x], owl_recap$y_1[x],
                                 owl_recap$x_2[x], owl_recap$y_2[x]), byrow = T, 
                               nrow = 2))
  return(pair)
})

#format lines into sfc object
recap_sfc <- st_sfc(recap_lines)

#merge sfc object with original data.frame
mult_recap <- st_sf(owl_recap, geom = recap_sfc, crs = 26913) %>% 
  st_transform("+init=epsg:4326")

#make points for first and second captures
owl_first <- st_as_sf(owl_recap, coords = c("x_1", "y_1"), crs = 26913) %>%   st_transform("+init=epsg:4326")
owl_second <- st_as_sf(owl_recap, coords = c("x_2", "y_2"), 
                       crs = 26913) %>% 
  st_transform("+init=epsg:4326")
#read in the hotel gulch boundary
hotel_bound <- st_read("gis/Hotel_Shp/hotel_boundary.shp", crs = 26913) %>% 
  st_transform("+init=epsg:4326") 

#read in trout creek boundary
trout_bound <- st_read("gis/trout_boundary.shp", crs = 26913) %>% 
  st_transform("+init=epsg:4326")

#read in mizzou boundary
miss_bound <- st_read("gis/missouri_boundary.shp", crs = 26913) %>% 
  st_transform("+init=epsg:4326")

#add hotel territories
hotel_terr <- st_read("gis/hotel_territories_2016.shp", crs = 26913) %>%
  st_transform(crs = 4326)

#make hayman boundary
hayman_bound <- st_sfc(st_polygon(x=list(matrix(c(476612, 4335175, 
                                                  476612, 4328660, 
                                                  484110, 4328660, 
                                                  484110, 4335175,
                                                  476612, 4335175), ncol = 2, byrow = T)))) %>% 
  st_set_crs(26913) %>% 
  st_transform("+init=epsg:4326")

#net locations
nets <- read.csv("data/net_locs.csv")
nets_sf <- st_as_sf(nets, coords = c("x", "y"), crs = 26913) %>%
  st_transform(crs = 4326)

#get google maps base layer
base <- get_map(center = c(lon = -105.1, lat = 39.1), zoom = 11, 
                maptype ="terrain", color = "bw")
```

Make maps:
```{r }
#make the fall to summer map
f2s_plot <- ggmap(base, darken = c(.3,"#FFFFFF")) +
  xlim(c(-105.1, -105)) +
  ylim(c(39.07, 39.18)) +
  coord_sf() +
  geom_sf(data = hotel_bound, inherit.aes = FALSE, fill  = NA, 
          linetype = "twodash", color = "black", size = 1.25) +
  geom_sf(data = miss_bound, inherit.aes = FALSE, fill  = NA, 
          linetype = "twodash", color = "black", size = 1.25) +
  geom_sf(data = mult_recap[mult_recap$cap_type == "f2s", ], 
          inherit.aes = FALSE, color = "black") +
  geom_sf(data = owl_first[mult_recap$cap_type == "f2s", ], 
          inherit.aes = FALSE, shape = 15, color = "black") +
  geom_sf(data = owl_second[mult_recap$cap_type == "f2s", ],
          inherit.aes = FALSE, shape = 24) +
  north(x.min = -105.1, x.max = -105.0, y.min = 39.07, y.max = 39.18, 
        location = "bottomleft") +
  # scalebar(x.min = -105.3, x.max = -105.01, y.min = 39.07, y.max = 39.18, 
  #          dist = 2, dist_unit = "km", st.bottom = FALSE, 
  #          st.color = "black", transform = TRUE, model = "WGS84", 
  #          st.dist = .05) +
  ggtitle("(A)") +
  theme_minimal() +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank())

#make natal dispersal map
nat_disp_plot <- ggmap(base, darken = c(.3,"#FFFFFF")) +
  xlim(c(-105.22, -105.03)) +
  ylim(c(39.07, 39.18)) +
  coord_sf() +
  geom_sf(data = hayman_bound, inherit.aes = FALSE, fill  = NA, 
          linetype = "twodash", color = "black", size = 1.25) +
  geom_sf(data = hotel_bound, inherit.aes = FALSE, fill  = NA, 
          linetype = "twodash", color = "black", size = 1.25) +
  geom_sf(data = trout_bound, inherit.aes = FALSE, fill  = NA, 
          linetype = "twodash", color = "black", size = 1.25) +
  geom_sf(data = miss_bound, inherit.aes = FALSE, fill  = NA, 
          linetype = "twodash", color = "black", size = 1.25) +
  geom_sf(data = mult_recap[mult_recap$cap_type == "s2f" & 
                              mult_recap$age_1 == "HY", ], 
          inherit.aes = FALSE, color = "black") +
  geom_sf(data = owl_first[mult_recap$cap_type == "s2f" & 
                             mult_recap$age_1 == "HY", ], 
          inherit.aes = FALSE, shape = 24, color = "black") +
  geom_sf(data = owl_second[mult_recap$cap_type == "s2f" &
                              mult_recap$age_1 == "HY", ],
          inherit.aes = FALSE, shape = 15, color = "black", fill = "#F0F8FF") +
  scalebar(x.min = -105.22, x.max = -105.03, y.min = 39.07, y.max = 39.18, 
           dist = 4, dist_unit = "km", st.bottom = FALSE, 
           st.color = "black", transform = TRUE, model = "WGS84", 
           st.dist = .05) +
  # north(x.min = -105.20, x.max = -105.15, y.min = 39.07, y.max = 39.2,
  #       location = "bottomleft") +
  theme_minimal() +
  ggtitle("(B)") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank())

dispplots <- arrangeGrob(grobs = list(f2s_plot, nat_disp_plot), 
                         widths = unit(c(2.2,4), c("in", "in")), 
                         layout_matrix = matrix(c(1,2), nrow = 1))

ggsave(dispplots, file = "figures/dispplots.png", dpi = 400)
```

Map that shows territories of breeders captured in the fall.

```{r}
(breeder_caps <- ggmap(base, darken = c(.3,"#FFFFFF")) +
   coord_sf() +
   geom_sf(data = hotel_bound, inherit.aes = FALSE, fill  = NA, 
           linetype = "twodash", color = "black", size = 1.25) +
   geom_sf(data = hotel_terr, inherit.aes = FALSE, linetype = "dashed",
           size = 1, color = "black",
           fill = NA) +
   #  scale_linetype_manual(values = c("A7" = "solid", "A15" = "solid",
   #                                  "A2" = "solid", "A8" = "solid",
   #                                  "A10" = "solid", "A18" = "solid",
   #                                  "A20" = "dashed", "A4" = "dashed",
   #                                  "A12" = "dashed", "A13" = "dashed",
   #                                  "A11" = "dashed", "A27" = "dashed",
   #                                  "A40" = "dashed", "A41" = "dashed", 
   #                                  "A43" = "dashed", "A44" = "dashed",
   #                                  "A29" = "dashed", "A24" = "dashed",
   #                                  "A45" = "dashed")) +
   geom_sf(data = mult_recap[mult_recap$cap_type == "s2f" &
                               mult_recap$age == "AHY" &
                               mult_recap$band %in% 
                               mult_recap$band[mult_recap$cap_type == "b2f2s"], ],
           inherit.aes = F, color = "black", aes(size = band)) +
   scale_size_manual(values = c("1783-64546" = 2, "1783-64541" = 2,
                                "1783-64465" = 1, "1783-64515" = 1,
                                "1783-64397" = 1, "1593-64747" = 1,
                                "1783-64506" = 1, "1783-64514" = 1)) +
   geom_sf(data = owl_first[owl_first$cap_type == "s2f" &
                              owl_first$age == "AHY" &
                              owl_first$band %in%
                              owl_first$band[owl_first$cap_type == "b2f2s"], ],
           inherit.aes = F, color = "black", shape = 24, size = 3) +
   geom_sf(data = owl_second[owl_second$cap_type == "s2f" &
                               owl_second$age == "AHY" &
                               owl_second$band %in%
                               owl_second$band[owl_second$cap_type == "b2f2s"], ],
           inherit.aes = F, color = "black", shape = 15, size = 3) +
   scalebar(x.min = -105.07, x.max = -105.025, y.min = 39.078, y.max = 39.106, 
            dist = 1, dist_unit = "km", st.bottom = FALSE, 
            st.color = "black", transform = TRUE, model = "WGS84", 
            st.dist = .04) +
   north(x.min = -105.07, x.max = -105.05, y.min = 39.078, y.max = 39.106, 
         location = "bottomleft") +
   scale_x_continuous(limits = c(-105.07, -105.025), 
                      breaks = seq(-105.07, -105.03, .02)) +
   scale_y_continuous(limits = c(39.078, 39.106), 
                      breaks = seq(39.08, 39.107, .01)) +
   theme_minimal() +
   theme(axis.text = element_blank(),
         axis.ticks = element_blank(),
         axis.title = element_blank(),
         legend.position = "none"))

```

Make study area map

```{r}
study_areas <- ggmap(base, darken = c(.3,"#FFFFFF")) +
  coord_sf() +
  geom_sf(data = hayman_bound, inherit.aes = FALSE, fill  = NA, 
          linetype = "twodash", color = "black", size = 1.25) +
  geom_sf(data = hotel_bound, inherit.aes = FALSE, fill  = NA, 
          linetype = "twodash", color = "black", size = 1.25) +
  geom_sf(data = trout_bound, inherit.aes = FALSE, fill  = NA, 
          linetype = "twodash", color = "black", size = 1.25) +
  geom_sf(data = miss_bound, inherit.aes = FALSE, fill  = NA, 
          linetype = "twodash", color = "black", size = 1.25) +
  # geom_text(aes(x = -105.05, y = 39.17, label = "MG")) +
  # geom_text(aes(x = -105.05, y = 39.11, label = "HG")) +
  # geom_text(aes(x = -105.225, y = 39.175, label = "HF")) +
  # geom_text(aes(x = -105.12, y = 39.055, label = "TC")) +
  scalebar(x.min = -105.3, x.max = -105.0, y.min = 39.0, y.max = 39.18, 
           dist = 4, dist_unit = "km", st.bottom = FALSE, 
           st.color = "black", transform = TRUE, model = "WGS84", 
           st.dist = .05) +
  north(x.min = -105.3, x.max = -105.0, y.min = 39.0, y.max = 39.18, 
        location = "bottomleft") +
  scale_x_continuous(limits = c(-105.3, -105.0), 
                     breaks = seq(-105.3, -105.0, .2)) +
  scale_y_continuous(limits = c(39.0, 39.18), breaks = seq(39.0, 39.18, .1)) +
  xlab("") +
  ylab("") +
  theme(axis.text = element_text(size = 14))

net_sites <- ggmap(base, darken = c(.3,"#FFFFFF")) +
  coord_sf() +
  geom_sf(data = hotel_bound, inherit.aes = FALSE, fill  = NA, 
          linetype = "twodash", color = "black", size = 1.25) +
  geom_sf(data = hotel_terr, inherit.aes = FALSE, size = 1, color = "black",
          fill = NA) +
  geom_sf(data = nets_sf, inherit.aes = F, shape = 15, size = 4) +
  scalebar(x.min = -105.07, x.max = -105.025, y.min = 39.078, y.max = 39.106, 
           dist = 1, dist_unit = "km", st.bottom = FALSE, 
           st.color = "black", transform = TRUE, model = "WGS84", 
           st.dist = .04) +
  north(x.min = -105.07, x.max = -105.025, y.min = 39.07, y.max = 39.106, 
        location = "bottomleft") +
  scale_x_continuous(limits = c(-105.07, -105.025), 
                     breaks = seq(-105.07, -105.03, .02)) +
  scale_y_continuous(limits = c(39.078, 39.106), 
                     breaks = seq(39.08, 39.107, .01)) +
  xlab("") +
  ylab("")

#US Map
#get US map of state boundaries
usa_states <- ne_states(returnclass = "sf", country = "united states of america")
#get US borders
us <- ne_countries(country = "united states of america", returnclass = "sp")

(usmap <- ggplot() +
    geom_sf(data = usa_states) + 
    xlim(125, 65) +
    #fix bug that won't let me remove grid lines with this...
    coord_sf(datum = NA) +
    theme_void())

ggsave(study_areas, file = "figures/study_area_fig/study_area.png", dpi = 400)
ggsave(net_sites, file = "figures/study_area_fig/net_ites.png", dpi = 400)
ggsave(usmap, file = "figures/study_area_fig/usa.png", dpi = 400)

```
# Session Info  
```{r}
sessionInfo()
```

